Measuring security performance in the Android ecosystem

### 2015-06-04 ccs.tex
Better meet EPSRC requirements for Acknowledgements and datatset

\sloppy
\section*{Acknowledgements}
\identifying{
This work was supported by a Google focussed research award and the EPSRC Standard Research Grant EP/P505445/1.
}
Some of the raw and processed data and source code will be made available.

>>>>

\section*{Dataset}
The raw and processed data and source code will be made available where possible.
Data from \da\ and \avo\ used in this paper is already available.

\sloppy
\section*{Acknowledgements}
\identifying{
This work was supported by a Google focussed research award; and the EPSRC [grant number EP/P505445/1].
}
